---
title: '1'
author: "Peizhao Wang"
date: "2022/6/15"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
#library a bunch of packages we may (or may not) use - install them first if not installed already. 
library(tidyverse)
library(tmap)
library(geojsonio)
library(plotly)
library(rgdal)
library(broom)
library(mapview)
library(crosstalk)
library(sf)
library(sp)
library(spdep)
library(car)
library(fs)
library(janitor)
library(ggplot2)
library(spatstat)
library(broom)
library(tidymodels)
library(usethis)
library(corrr)
```

```{r}
library(mosaic)  # standardizing variables
```


```{r}
LondonWardProfiles <- read_csv(here::here('data','out2.csv'), 
                               na = c("", "NA", "n/a"), 
                               col_names = TRUE)

```

```{r}
Londonwards <- st_read(here::here("data", "statistical-gis-boundaries-london", "statistical-gis-boundaries-london","ESRI", "London_Ward_CityMerged.shp"))
```

```{r}
qtm(Londonwards)
```

```{r}
#check all of the columns have been read in correctly
Datatypelist <- LondonWardProfiles %>% 
  summarise_all(class) %>%
  pivot_longer(everything(), 
               names_to="All_variables", 
               values_to="Variable_class")

Datatypelist
```
```{r}
#merge boundaries and data
LonWardProfiles <- Londonwards%>%
  left_join(.,
            LondonWardProfiles, 
            by = c("GSS_CODE" = "New Code"))
```

```{r}
#let's map our dependent variable to see if the join has worked:
tmap_mode("plot")
qtm(LonWardProfiles, 
    fill = "Children_Poverty_Rate", 
    borders = NULL,  
    fill.palette = "Blues")
```

```{r}
symbox(~ Children_Poverty_Rate, 
       LonWardProfiles, 
       na.rm=T,
       powers=seq(-3,3,by=.5))
```
```{r}
symbox(~ E1, 
       LonWardProfiles, 
       na.rm=T,
       powers=seq(-3,3,by=.5))

```



```{r}
library(corrr)

Correlation <- LonWardProfiles %>%
  st_drop_geometry()%>%
  dplyr::select(Children_Poverty_Rate,
         E1,
         E2,
         E3,
         E4,
         E5,
         E6,
         HD1,
         HD2,
         L1,
         L2,
         O,
         P1,
         P2,
         P3,
         Q)%>%
    correlate() %>%
  # just focus on Children_Poverty_Rate
  focus(-Children_Poverty_Rate, mirror = TRUE) 


#visualise the correlation matrix
rplot(Correlation)
```

```{r}
Datatypelist
```



```{r}
Regressiondata1<- LonWardProfiles%>%
  st_drop_geometry()%>%

  dplyr::select(Children_Poverty_Rate, 
         E1,
         E2,
         E3,
         E4,
         E5,
         E6,
         HD1,
         HD2,
         L1,
         L2,
         O,
         P1,
         P2,
         P3,
         Q)
```



```{r}
model1 <- LonWardProfiles %>%
  lm(Children_Poverty_Rate ~ 
       E3+
       E4+
       E6+
       O+
       Q, data =.)

#show the summary of those outputs
tidy(model1)
```
```{r}
glance(model1)
```
```{r}
res1 <- resid(model1)
```

```{r}
plot(fitted(model1), res1)
```



```{r}
position <- c(10:24)

Correlation_all<- LonWardProfiles %>%
  st_drop_geometry()%>%
  dplyr::select(position)%>%
    correlate()

rplot(Correlation_all)
```
# using the stepwise regression dimension reduced data
```{r}
Regressiondata2<- LonWardProfiles%>%
  dplyr::select(Children_Poverty_Rate,
       E3,
       E4,
       E6,
       O,
       Q)

```

```{r}
position <- c(2:6)

Correlation_all<- Regressiondata2 %>%
  st_drop_geometry()%>%
  dplyr::select(position)%>%
    correlate()

rplot(Correlation_all)
```



```{r}
model2 <- LonWardProfiles %>%
  lm(Children_Poverty_Rate ~ 
       scale(E3)+
       scale(E4)+
       scale(E6)+
       scale(O)+
       scale(Q), data =.)

#show the summary of those outputs
tidy(model2)
```
# all variables are reliable

```{r}
glance(model2)
```

```{r}
tidy(durbinWatsonTest(model2))
```
# The Durbin-Watson Test result is not significant.

```{r}
res <- resid(model2)
```

```{r}
plot(fitted(model2), res)
```

# The statistic is very close to 2, indicating very small positive autocorrelation.
## Because the p-value is less than 0.05, it cannot indicate that there is autocorrelation

```{r}
droped_London_poverty_merged_file <-     LonWardProfiles %>%
  drop_na()
```

```{r}
droped_London_poverty_merged_file_with_residual <- droped_London_poverty_merged_file %>%
  mutate(.,res)
```


```{r}
tmap_mode("view")
tm_shape(droped_London_poverty_merged_file_with_residual) +
  tm_polygons("res",
              palette = "RdYlBu")
```
# residuals are mostly from -5 to 5, following a normal distribution. Meaning that the regression is feasible.


```{r}
#calculate the centroids of all Wards in London
coordsW <- droped_London_poverty_merged_file_with_residual%>%
  st_centroid()%>%
  st_geometry()

plot(coordsW)
```

```{r}
#Now we need to generate a spatial weights matrix 
#(remember from the lecture a couple of weeks ago). 
#We'll start with a simple binary matrix of queen's case neighbours

LWard_nb <- droped_London_poverty_merged_file_with_residual %>%
  poly2nb(., queen=T)

#or nearest neighbours
knn_wards <-coordsW %>%
  knearneigh(., k=4)

LWard_knn <- knn_wards %>%
  knn2nb()

#plot them
plot(LWard_nb, st_geometry(coordsW), col="red")
```
test Moran's I  to check spatial autocorrelation
```{r}
Lward.lw <- LWard_nb %>%
  nb2listw(., style="C")
```

```{r}
I_LWard_Global_Density <- droped_London_poverty_merged_file_with_residual %>%
  pull(Children_Poverty_Rate) %>%
  as.vector()%>%
  moran.test(., Lward.lw)

I_LWard_Global_Density
```
The statistic value is more close to 1 other than -1. This means there are cluster with similar values. 


```{r}
#create a spatial weights matrix object from these weights
Lward.queens_weight <- LWard_nb %>%
  nb2listw(., style="W")

Lward.knn_4_weight <- LWard_knn %>%
  nb2listw(., style="W")
```

```{r}
Queen <- droped_London_poverty_merged_file_with_residual %>%
  st_drop_geometry()%>%
  dplyr::select(res)%>%
  pull()%>%
  moran.test(., Lward.queens_weight)%>%
  tidy()
```


#to test the local spatail regression models. Which might has a better performance.


```{r}
library(spgwr)

coordsW2 <- st_coordinates(coordsW)

droped_London_poverty_merged_file_with_residual2 <- cbind(droped_London_poverty_merged_file_with_residual,coordsW2)
```



```{r}
GWRbandwidth <- gwr.sel(Children_Poverty_Rate ~ 
       scale(E3)+
       scale(E4)+
       scale(E6)+
       scale(O)+
       scale(Q),   
                  data = droped_London_poverty_merged_file_with_residual2, 
                        coords=cbind(droped_London_poverty_merged_file_with_residual2$X, droped_London_poverty_merged_file_with_residual2$Y),
                  adapt=T)
```

```{r}
GWRbandwidth
```

```{r}
#run the gwr model
gwr.model = gwr(Children_Poverty_Rate ~ 
       scale(E3)+
       scale(E4)+
       scale(E6)+
       scale(O)+
       scale(Q), 
                  data = droped_London_poverty_merged_file_with_residual2, 
                coords=cbind(droped_London_poverty_merged_file_with_residual2$X, droped_London_poverty_merged_file_with_residual2$Y), 
                adapt=GWRbandwidth,
                #matrix output
                hatmatrix=TRUE,
                #standard error
                se.fit=TRUE)

#print the results of the model
gwr.model
```
# The GWR's R-squared value is 0.9826
# Comparing with other models, GWR comes to have better performance than standardized regression.

```{r}
results <- as.data.frame(gwr.model$SDF)
names(results)
```





```{r}
#attach coefficients to original SF


droped_London_poverty_merged_file_with_residual3 <- droped_London_poverty_merged_file_with_residual2 %>%
  mutate(
         coefE3 = results$scale.E3.,
         coefE4 = results$scale.E4.,
         coefE6 = results$scale.E6.,
         coefO = results$scale.O.,
         coefQ = results$scale.Q.)
```






```{r}
tm_shape(droped_London_poverty_merged_file_with_residual3) +
  tm_polygons(col = "coefE3", 
              palette = "RdBu", 
              alpha = 0.5)
```


```{r}
tm_shape(droped_London_poverty_merged_file_with_residual3) +
  tm_polygons(col = "coefE4", 
              palette = "RdBu", 
              alpha = 0.5)
```

```{r}
tm_shape(droped_London_poverty_merged_file_with_residual3) +
  tm_polygons(col = "coefE6", 
              palette = "RdBu", 
              alpha = 0.5)
```

```{r}
tm_shape(droped_London_poverty_merged_file_with_residual3) +
  tm_polygons(col = "coefO", 
              palette = "RdBu", 
              alpha = 0.5)
```


```{r}
tm_shape(droped_London_poverty_merged_file_with_residual3) +
  tm_polygons(col = "coefQ", 
              palette = "RdBu", 
              alpha = 0.5)
```





